%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Research \& Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {RESEARCH INTERN -- PROBABILISTIC GRAPHICAL MODELS} % Job title
    {LIP6 Laboratory (Laboratoire d'Informatique de Paris 6), Sorbonne Universit\'{e}} % Organization
    {Paris, France} % Location
    {Feb. 2025 -- June 2025} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed a T-order Dynamic Bayesian Network (DBN) using Python and pyAgrum.}
        \item {Developed custom inference algorithms for complex temporal dependencies.}
        \item {Optimized performance to mitigate combinatorial explosion in high-dimensional models.}
        \item {Applied measure theory and probability to validate model consistency.}
      \end{cvitems}
    }

%---------------------------------------------------------
\vspace{-3mm}
  \cventry
    {GPU-ACCELERATED FINBERT FINE-TUNING}
    {Personal Project -- NLP \& Quantitative Finance}
    {}
    {Jan. 2025 -- Present}
    {
      \begin{cvitems}
        \item {Fine-tuned FinBERT on the Financial PhraseBank dataset (100\% annotator agreement) for financial sentiment classification.}
        \item {Optimized training pipeline for local GPU execution on an NVIDIA RTX 3060 (fp16 mixed precision, gradient accumulation).}
        \item {Delivered 3-class sentiment classification (Positive / Negative / Neutral) using the HuggingFace Transformers stack.}
      \end{cvitems}
    }

%---------------------------------------------------------
\vspace{-3mm}
  \cventry
    {CPU ARCHITECTURE SIMULATOR} % Job title
    {Data Structures course project, Sorbonne Universit\'{e}} % Organization
    {Paris, France} % Location
    {March 2025 -- June 2025} % Date(s)
    {
      \begin{cvitems}
        \item {Designed and implemented a functional CPU simulator modeling the fetch-decode-execute cycle and instruction set architecture.}
        \item {Developed low-level memory management and register simulation to ensure binary compatibility with custom assembly.}
        \item {Optimized execution logic in C to handle complex instruction flows and pipeline states.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
